---
title: "PSY 6937"
subtitle: "Colloquium in Psychological Research"
author: "Visualizing Data"
output:
  ioslides_presentation:
    css: styles.css
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#Load the foreign package so we can import an SPSS file
if (!require(foreign)){
  install.packages("foreign", dependencies = TRUE)
  require(foreign)
}

if (!require(ggplot2)){
  install.packages("ggplot2", dependencies = TRUE)
  require(ggplot2)
}
```
## Reproducible Science (Presentations)
- **If I re-analyze your data, do I get the same results?**

[In the journal cognition](http://rsos.royalsocietypublishing.org/content/5/8/180448):

>- About 78% of data is available to be re-analyzed
>- About 60% of data is actually usable
>- Of 35 articles selected for a test:
>- 11 could be reproduced
>- 11 more could be reproduced with help from the authors
>- 13 articles not be reproduced even with author help

## Reproducible Science (Presentations) 2

>- Use RStudio to create manuscripts
>- Code to produce statistics in manuscript is included in .RMD file
>- 'Knit' to create the pdf
>- [papaja](https://github.com/crsh/papaja)
>- [bookdown](https://bookdown.org)

## Reproducible Science (Presentations) 3

>- Presentations are another communication method that would benefit from reproducibility
>- Have you ever created a figure for a presentation then been unable to recreate to analysis the figure was based on when writing the manuscript (months later)
>- [ioslides](https://rmarkdown.rstudio.com/ioslides_presentation_format)

## [ioslides](https://rmarkdown.rstudio.com/ioslides_presentation_format)

- File -> New File -> R Markdown...
- Select presentation tab
- Select ioslides
- Type name of presentation
- Press OK

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with Bullets that appear on click

>- Bullet 1
>- Bullet 2
>- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

## Slide with table
|Fuzzy verbs (weak)|Action Verbs (Strong)|
|:----------------:|:-------------------:|
|occur             |modify               |
|facilitate        |increase/decrease    |
|conduct           |accomplish           |
|implement         |create               |
|affect            |invade               |
|perform           |react                |
|                  |inhibit              |
|                  |disrupt              |
|                  |accelerate           |
|                  |migrate              |

## Slide with circles

<div class="circle-text">Design</div>
<div class="circle-text" >Collect</div>
<div class="circle-text" >Analyze</div>
<div class="circle-text-emphasis" >Replicate</div>

## Class Presentation Information

- Create ioslides presentation
- Do not present it
- You must use a custom css file to create a custom 'look' for your presentation. Do not use the default or my garish color scheme.
- Add presenter notes to each slide. I want to read the presentation you won't give. This slide has an example of hidden presenter notes

<div class="notes">
This is where you put your presenter notes for each slide. They won't appear on the main screen.
</div>


## Class presentation slides
- Use the following slides:
    - Title Slide with name
    - Interest slide(s)
    - Background slide(s)
    - What do you want to learn? slide
    - How do you plan to learn it? slide 
    - What do you think will happen? slide 
    - Conclusion slide
        - Synopsis of key results
        - How do they answer your question
        - What does this contribute to larger problem
    - Final slide--Thank you, take-home message, link to OSF, pre-registration

## Tips for making graphs
- Contrast
    - Use colors and solid lines when appropriate (powerpoint or web)
- Think about the order you present categories
    - High to low
    - alphabetical
    - Use the same order you've been using throughout your talk/paper
- Spacing between bars should be half the bars' width
- Set up side by side comparisons
- no 3d, no pie charts


## Creating a plot
[Esquisse](https://github.com/dreamRs/esquisse)

```{r echo=TRUE}
# From CRAN
if (!require(esquisse)){
  install.packages("esquisse", dependencies = TRUE)
  require(esquisse)
}
```


## Example Predictions slide

```{r warning=FALSE, echo=FALSE}
#load the SPSS file into a variable called 'dataset.' Now I can access the SPSS file just by referring to 'dataset'
dataset = read.spss("https://osf.io/b2359/download", to.data.frame=TRUE, use.value.labels = FALSE)

(ggplot(dataset, aes(Comp1, AscentOfHumans_2)) + 
  geom_jitter(alpha = .4, 
              size = 5, 
              color = "#B4975A") + 
  geom_smooth(method = lm, 
              color="#B4975A", 
              fill = "#A1A1A4", 
              linetype="dashed") + 
  labs(x = "How competent you believe society views Black people", 
       y = "How evolved do you believe Black people are?")  + 
  theme_minimal() + 
  theme(axis.line = element_line(color="#B4975A", size = .5), 
        panel.grid = element_blank(),
        plot.background = element_rect(fill = "#061922"), 
        axis.title = element_text(color="#B4975A"), 
        axis.text=element_text(color = "#B4975A")) + 
  annotate("text", label = "r = .22", x = 5, y = 25, color="#B4975A", size=10) -> myggplot)
```

## Saving directly to powerpoint
```{r echo=TRUE}
if (!require(rvg)){
  install.packages("rvg", dependencies = TRUE)
  require(rvg)
}

if (!require(officer)){
  install.packages("officer", dependencies = TRUE)
  require(officer)
}
```

## Saving directly to powerpoint 2
```{r echo=TRUE}
doc <- read_pptx()
doc <- add_slide(doc, layout = "Title and Content", master = "Office Theme")
doc <- ph_with_gg(doc, value = myggplot)
print(doc, target = "my_plot.pptx")
```

## Saving as .png
```{r echo=TRUE}
ggsave("myplot.png", plot = myggplot)
```



